Contextual Combinatorial Cascading Bandits

### 2015-12-03 contextual combinatorial cascading bandits.tex
update notation of history and conditional expectation

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set of $L$ ground items,  $E=\{1,...,L\}$, also referred to as {\em base arms}. 
Let $\prod^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$. We also refer to each of such tuples as an {\em action}.
Let $\cS \subseteq \cup_{k=1}^K \prod^{k}$ be the set of feasible actions with length no more than $K$.

@@

Assume $\bw_{t,a}$'s are mutually independent and satisfy
\wei{Is this given $x_{t,a}$ accurate? $x_{t,a}$  is not a probabilistic event. Also, are we assuming $\bw_{t,a}$'s are
		also independent of all other events, such as the event before time $t$? We should make it clear.
Perhaps we should put the history definition here?}
\begin{equation}
\label{eq:expectation}
\EE[\bw_{t,a} | x_{t,a}] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is,
	for some $k=1,2,\ldots, \abs{\bA_t}$, 
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$
At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.

@@

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. Here we abuse the notation $\abs{\bA_s}$ to denote the number of base arms in the action $\bA_s$. By Equation \eqref{eq:expectation}, we have 
$$
\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
\{(\gamma_k X_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. In the following, we will mainly use notations for disjunctive objective when the two cases are similar.

@@

So if the chosen action $\bA_t$ is not suboptimal, which means
$$
f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t), ~~ f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(\bA_t, \bU_t).
$$
Then we can derive an estimate of $\Delta_{t, \bA_t}$ and $\Delta_{\wedge, t, \bA_t}$, however, in terms of all base arms in $\bA_t$. Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate
\begin{align*}
&~~\EE_t[\Delta_{t, \bA_t}] \\
&= \EE[\Delta_{t, \bA_t}(1/p_{t, \bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}],\\
&~~\EE_t[\Delta_{\wedge, t, \bA_t}] \\
&= \EE[\Delta_{\wedge, t, \bA_t}(1/p_{\wedge, t, \bA_t}) \bOne\{\Delta_{\wedge, t, \bA_t} > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
\end{align*}

@@

\begin{lemma}
\label{lem:prefixRelation}
Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the conjunctive case, it holds that
$$
p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
$$
Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the disjunctive case and $k < \abs{A}$, we have the following properties:
\begin{itemize}
\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
\end{itemize}
\end{lemma}

\begin{proof}
It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$. First, for the conjunctive objective,
$$
f(A, w) \geq \gamma_{m} (1 - p_{A} + p_{A} w_{m}) \geq \gamma_{m} (1 - p_{A}).
$$
Then for the disjunctive objective,
\begin{itemize}
\item[(1)]
\begin{align*}
f_{\wedge}(A, w) &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
&\leq \gamma_m' + (1 - \gamma_m') p_{\wedge, A};
\end{align*}

@@

\begin{proposition}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for any time $t$. If we have
$$
\gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad \gamma_K' \geq \frac{1}{4} f_{\wedge}^{\ast}
$$
for some positive integer $n_0$, then
\begin{align*}
&E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[\Delta_{\wedge, t, \bA_t}|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
\end{align*}
where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
\end{proposition}
\begin{proof}
For the conjunctive case, $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the disjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$. Then we have
$$
\EE[\Delta_{\wedge, t, \bA_t} | \cH_{t-1}] \leq \frac{8}{f_{\wedge, t}^*} \EE[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by lemma \ref{lem:estimateTech}, we have
$$
\Delta_{\bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k' x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

@@

For the conjunctive case,
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \sum_{t=1}^{T} (n_0 + 1) \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq (n_0 + 1) \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
&\leq O(n_0 d \log(C_\gamma T)\sqrt{TK}).
\end{split}
\end{equation}

For the disjunctive case, 
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{\wedge, t, \bA_t}] \\
&\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
&\leq \frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq \frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \EE[\sqrt{(\sum_{t=1}^{T} \bO_t) (\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)}]\\
&\leq O(\frac{d}{f_{\wedge}^{\ast}}\log(C_\gamma T)\sqrt{TK}).
\end{split}
\end{equation}
\end{proof}

>>>>

We formulate the problem of {\em contextual combinatorial cascading bandit} as follows. Suppose we have a finite set of $L$ ground items,  $E=\{1,...,L\}$, also referred to as {\em base arms}. 
Let $\prod^k=\{(a_1,...,a_k): a_1,...,a_k \in E, a_i \neq a_j \text{ for any } i \neq j\}$ be the set of all $k$-tuples of distinct items from $E$. We also refer to each of such tuples as an {\em action}.
Let $\cS \subseteq \cup_{k=1}^K \prod^{k}$ be the set of feasible actions with length no more than $K$. As a convention, we use boldface symbols to represent all random variables.

@@

Let $\cH_t$ denote all history before the learning agent chooses action at time $t$; $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\wei{Is this given $x_{t,a}$ accurate? $x_{t,a}$  is not a probabilistic event. Also, are we assuming $\bw_{t,a}$'s are
		also independent of all other events, such as the event before time $t$? We should make it clear.
Perhaps we should put the history definition here?}
\begin{equation}
\label{eq:expectation}
\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is,
	for some $k=1,2,\ldots, \abs{\bA_t}$, 
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$
At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$.

@@

Because $\cH_t$ denotes all history before time $t$ and context information of time $t$, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s<t, x_t \}$ and define $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. Here we abuse the notation $\abs{\bA_s}$ to denote the number of base arms in the action $\bA_s$. By Equation \eqref{eq:expectation}, we have 
$$
\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
\{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. In the following, we will mainly use notations for disjunctive objective when the two cases are similar.

@@

So if the chosen action $\bA_t$ is not suboptimal, which means
$$
f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t), ~~ f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(\bA_t, \bU_t).
$$
Then we can derive an estimate of $\Delta_{t, \bA_t}$ and $\Delta_{\wedge, t, \bA_t}$, however, in terms of all base arms in $\bA_t$. Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate
\begin{align*}
&~~\EE_t[\Delta_{t, \bA_t}] \\
&= \EE_t[\Delta_{t, \bA_t}(1/p_{t, \bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}],\\
&~~\EE_t[\Delta_{\wedge, t, \bA_t}] \\
&= \EE_t[\Delta_{\wedge, t, \bA_t}(1/p_{\wedge, t, \bA_t}) \bOne\{\Delta_{\wedge, t, \bA_t} > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
\end{align*}

@@

\begin{lemma}
\label{lem:prefixRelation}
Suppose 
% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
% For the conjunctive case, it holds that
% $$
% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
% $$
Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with disjunctive objective and $k < \abs{A}$, we have the following properties:
\begin{itemize}
\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
\end{itemize}
\end{lemma}

\begin{proof}
% It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$. First, for the conjunctive objective,
% $$
% f(A, w) \geq \gamma_{m} (1 - p_{A} + p_{A} w_{m}) \geq \gamma_{m} (1 - p_{A}).
% $$
% Then for the disjunctive objective,
\begin{itemize}
\item[(1)]
\begin{align*}
f_{\wedge}(A, w) &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
&\leq \gamma_m' + (1 - \gamma_m') p_{\wedge, A};
\end{align*}

@@

\begin{proposition}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \geq \frac{1}{4} f_{\wedge}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[\Delta_{\wedge, t, \bA_t}|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
\end{align*}
where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
\end{proposition}
\begin{proof}
For the conjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the disjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$. Then we have
$$
\EE_t[\Delta_{\wedge, t, \bA_t}] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by lemma \ref{lem:estimateTech}, we have
$$
\Delta_{\wedge, t, \bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

@@

For the conjunctive case,
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]]\\
&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
&\leq O(\frac{d}{p^*} \log(C_\gamma T)\sqrt{TK}).
\end{split}
\end{equation}

For the disjunctive case, 
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[\Delta_{\wedge, t, \bA_t}] \\
&\leq \EE[\sum_{t=1}^{T} \frac{8}{f_{\wedge}^{\ast}} \EE_t[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}] \\
&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq \EE[\frac{8}{f_{\wedge}^{\ast}} \beta_{T}(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE_t[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}]\\
&\leq O(\frac{d}{f_{\wedge}^{\ast}}\log(C_\gamma T)\sqrt{TK}).
\end{split}
\end{equation}
\end{proof}
